Synthesizing Verified Components for Cyber Assured Systems Engineering \thanks{DISTRIBUTION STATEMENT A. Approved for public release.}

### 2022-12-08 paper/abstract.tex
Revise abstract and intro and sout moved paragraphs in section 2

\newjunk{%
Avionics need to be engineered to be cyber-resilient meaning that systems are able to detect and recover from attacks or safely shutdown.
%
As there are few development tools for cyber-resiliency, designers rely on guidelines and checklists, sometimes missing vulnerabilities until late in the process where remediation is expensive.
%
Our solution is a model-based approach with cyber-resilience-improving transforms that insert high-assurance components such as filters to block malicious data or monitors to detect and alarm anomalous behavior.
%
Novel is our use of model checking and a verified compiler to specify, verify, and synthesize these components.
%
We define \emph{code contracts} as formal specifications that designers write for high-assurance components, and \emph{test contracts} as tests to validate their behavior.
%
A model checker proves whether or not code contracts satisfy test contracts in an iterative development cycle.
%
The same model checker also proves whether or not a system with the inserted components, assuming they adhere to their code contracts, provide the desired cyber-resiliency for the system.
%
We define an algorithm to synthesize implementations for code contracts in a semantics-preserving way that is backed by a verified compiler.
%
The entire workflow is implemented as part of the open source \emph{\brfcs} toolkit.
%
We report on our experience using \brfcs\ with a case study on a UAV system that is transformed to be cyber-resilient to communication and supply chain cyber attacks.
%
Our case study demonstrates that synthesizing correct implementations from code
contracts is feasible in real-world systems engineering.
}

>>>>

\newjunk{%
Avionics need to be engineered to be cyber-resilient meaning that systems are able to detect and recover from attacks or safely shutdown.
%
As there are few development tools for cyber-resiliency, designers rely on guidelines and checklists, sometimes missing vulnerabilities until late in the process where remediation is expensive.
%
Our solution is a model-based approach with cyber-resilience-improving transforms that insert high-assurance components such as filters to block malicious data or monitors to detect and alarm anomalous behavior.
%
Novel is our use of model checking and a verified compiler to specify, verify, and synthesize these components.
%
We define \emph{code contracts} as formal specifications that designers write for high-assurance components, and \emph{test contracts} as tests to validate their behavior.
%
A model checker proves whether or not code contracts satisfy test contracts in an iterative development cycle.
%
The same model checker also proves whether or not a system with the inserted components, assuming they adhere to their code contracts, provide the desired cyber-resiliency for the system.
%
We define an algorithm to synthesize implementations for code contracts in a semantics-preserving way that is backed by a verified compiler.
%
The entire workflow is implemented as part of the open source \emph{\brfcs} toolkit.
%
We report on our experience using \brfcs\ with a case study on a UAV system that is transformed to be cyber-resilient to communication and supply chain cyber attacks.
%
Our case study demonstrates that writing code contracts and then synthesizing correct implementations from them is feasible in real-world systems engineering for cyber-resilience.
}

### 2022-12-08 paper/overview.tex
Revise abstract and intro and sout moved paragraphs in section 2

The contributions of this paper relate to the aspects of
\brfcs\ concerning evidence that a high-assurance component meets its
intended purpose and is properly implemented.  This paper defines a
\emph{code contract} language that is a subset of the \agr\ language
with sequential evaluation semantics as opposed to the existing
parallel semantics of \agr.  The sequential semantics are requisite to
code synthesis and are defined such that \agr\ is able to still prove
consistency in the contract composition of the model.

This paper further defines a notion of \emph{test contract} for unit
testing code contracts outside of the system composition to verify
input to output behavior as well as general properties of the code
contract.  In practice, the behavior of a high assurance component is
defined by the designer in a code contract, and then using the
existing \agr\ model checker, test contracts prove the desired code
contract behavior.  Once the designer is satisfied that the code
contract is correct, the system composition is verified to conclude
that the contract meets the original cyber-requirement.

Showing that a component is properly implemented is accomplished
through formal synthesis from the code contract (bottom of
\figref{fig:tool-arch}).  This paper presents the Semantic Properties
of Language and Automata Theory (\splt) tool that generates
\emph{\ckml} code to implement the code contract.  \ckml\ is a
functional language that includes additional proofs and tools built
around it \cite{cakeml}.  The \ckml\ compiler itself is verified to
generate binary implementations that are equivalent in semantics to
the original input program.  That proof ensures that the resulting
binary exactly preserves the meaning of the original code contract and
assures that the component is faithfully implemented.

>>>>

\oldjunk{
The contributions of this paper relate to the aspects of
\brfcs\ concerning evidence that a high-assurance component meets its
intended purpose and is properly implemented.  This paper defines a
\emph{code contract} language that is a subset of the \agr\ language
with sequential evaluation semantics as opposed to the existing
parallel semantics of \agr.  The sequential semantics are requisite to
code synthesis and are defined such that \agr\ is able to still prove
consistency in the contract composition of the model.
}

\oldjunk{
This paper further defines a notion of \emph{test contract} for unit
testing code contracts outside of the system composition to verify
input to output behavior as well as general properties of the code
contract.  In practice, the behavior of a high assurance component is
defined by the designer in a code contract, and then using the
existing \agr\ model checker, test contracts prove the desired code
contract behavior.  Once the designer is satisfied that the code
contract is correct, the system composition is verified to conclude
that the contract meets the original cyber-requirement.
}

\oldjunk{
Showing that a component is properly implemented is accomplished
through formal synthesis from the code contract (bottom of
\figref{fig:tool-arch}).  This paper presents the Semantic Properties
of Language and Automata Theory (\splt) tool that generates
\emph{\ckml} code to implement the code contract.  \ckml\ is a
functional language that includes additional proofs and tools built
around it \cite{cakeml}.  The \ckml\ compiler itself is verified to
generate binary implementations that are equivalent in semantics to
the original input program.  That proof ensures that the resulting
binary exactly preserves the meaning of the original code contract and
assures that the component is faithfully implemented.
}
